CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-10-01 codecheck-paper.tex
add idea about independence from financial models of journals
codecheck for independent journals

The codecheckers community\footnote{\href{https://github.com/codecheckers/codecheckers/}{https://github.com/codecheckers/codecheckers/}}
currently has over 20 individuals who signed up as volunteer codecheckers
following talks given on the project in the last 12 months.
That is even though no checks are actively elicited.
We see a high potential in an open shared list of potential codecheckers 
compared to a private, in-house group, as it may better match expertise
and share the workload.
% TODO tell more about the motivations and commitments that we know about?

@@

\begin{itemize}
\item
  CODECHECK works! we have created 23 certificates to demonstrate it.
\item 
  CODECHECK and can increase trust in results, underlies the same
  limitations as peer review (needs people with time), but also the same
  power (community, reasoning of human)
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When some journals have it - what are crucial decisions/pain points?
  How open do they make the check itself and its outputs, and how does it
  relate/influence the openness of regular peer review
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\end{itemize}

>>>>

The codecheckers community\footnote{\href{https://github.com/codecheckers/codecheckers/}{https://github.com/codecheckers/codecheckers/}}
currently has over 20 individuals who signed up as volunteer codecheckers
following talks given on the project in the last 12 months.
That is even though no checks are actively elicited.
We see a high potential in an open shared list of potential codecheckers 
compared to a private, in-house group, as it may better match expertise
and share the workload.
% TODO tell more about the motivations and commitments that we know about?
The overarching community is also a mean to ensure CODECHECK is a viable
option not just for large publishers, independent of their financial model,
but also for independent no-cost open access journals.

@@

\begin{itemize}
\item
  CODECHECK works! we have created 23 certificates to demonstrate it.
\item 
  CODECHECK and can increase trust in results, underlies the same
  limitations as peer review (needs people with time), but also the same
  power (community, reasoning of human)
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When some journals have it - what are crucial decisions/pain points?
  How open do they make the check itself and its outputs, and how does it
  relate/influence the openness of regular peer review
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\item
  codecheck allows innovation independent of finance model of the journal
  and current peer review practices; evolutionary now, the "norm" later
\end{itemize}
